Supporting Information : Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-08-22 SuppMat.Rmd
writing discussion
moderate tail dep. code added

#initiate a dataframe to store ext risk at dispersal d=0 for all r
ricker_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) 
colnames(ricker_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

    ricker_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    ricker_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_ricker_global)<-list(NULL,cnm,anm)
saveRDS(res_ricker_global,paste(resloc,"res_ricker_global.RDS",sep=""))
```

@@

pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(ss$d, ss$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="darkgrey")
 # lines(ss$d, ss$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
 # mtext("Avg. ACF",side=4,line=3.2,col="green4") 
 # axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
  #---------------------------------------------------------
}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

ricker_extrisk_d0<-readRDS(paste(resloc,"ricker_extrisk_d0.RDS",sep=""))
numsims<-10000
ricker_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims
ricker_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_left_d0)/numsims

ricker_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_right_d0)/numsims
ricker_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_right_d0)/numsims

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

hassell_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(hassell_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

    hassell_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

```{r fig_hassell_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

hassell_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_left_d0)/numsims
hassell_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_left_d0)/numsims

hassell_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_right_d0)/numsims
hassell_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_right_d0)/numsims

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

msmith_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(msmith_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_msmith_local<-abind(res_msmith_local,temp_mat,along = 3)

    msmith_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_msmith_global<-abind(res_msmith_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_global)<-list(NULL,cnm,anm)
saveRDS(res_msmith_global,paste(resloc,"res_msmith_global.RDS",sep=""))
```

>>>>

#initiate a dataframe to store ext risk at dispersal d=0 for all r
ricker_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist)),
                              NA*numeric(length(rlist)),NA*numeric(length(rlist))) 
colnames(ricker_extrisk_d0)<-c("r","risk_xleft_d0","risk_xright_d0","risk_mleft_d0","risk_mright_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

    ricker_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    ricker_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]

    ricker_extrisk_d0$risk_mleft_d0[i]<-ss$risk_mleft[1]
    ricker_extrisk_d0$risk_mright_d0[i]<-ss$risk_mright[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_ricker_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_ricker_global)<-list(NULL,cnm,anm)
saveRDS(res_ricker_global,paste(resloc,"res_ricker_global.RDS",sep=""))
```

@@

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_ext_risk_local_disp_extremenoise.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)

}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp_extremenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_ext_risk_local_disp_moderatenoise.pdf",sep=""),height=9,width=9)

op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)

}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

ricker_extrisk_d0<-readRDS(paste(resloc,"ricker_extrisk_d0.RDS",sep=""))
numsims<-10000
ricker_extrisk_d0$CI0.025xleft<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_xleft_d0)/numsims
ricker_extrisk_d0$CI0.975xleft<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_xleft_d0)/numsims

ricker_extrisk_d0$CI0.025xright<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_xright_d0)/numsims
ricker_extrisk_d0$CI0.975xright<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_xright_d0)/numsims

ricker_extrisk_d0$CI0.025mleft<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_mleft_d0)/numsims
ricker_extrisk_d0$CI0.975mleft<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_mleft_d0)/numsims

ricker_extrisk_d0$CI0.025mright<-qbinom(p=0.025,size=numsims,prob=ricker_extrisk_d0$risk_mright_d0)/numsims
ricker_extrisk_d0$CI0.975mright<-qbinom(p=0.975,size=numsims,prob=ricker_extrisk_d0$risk_mright_d0)/numsims

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xleft,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975xleft,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025xright,x1=ricker_extrisk_d0$r,
       y1=ricker_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mleft_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mleft,x1=ricker_extrisk_d0$r,
       y1=ricker_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted",col="darkgrey") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025mright,
       x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Ricker"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("K = ",K),side = 3, line=-16, adj=0.95, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", legend=c("Ricker",paste0("K = ",K)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

hassell_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist)),
                               NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store 
                                                                       # ext risk at dispersal d=0 for all r
colnames(hassell_extrisk_d0)<-c("r","risk_xleft_d0","risk_xright_d0","risk_mleft_d0","risk_mright_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

    hassell_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    hassell_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_hassell_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

```{r fig_hassell_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_ext_risk_local_disp_extremenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp_extremenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_ext_risk_local_disp_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mright,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

hassell_extrisk_d0$CI0.025xleft<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_xleft_d0)/numsims
hassell_extrisk_d0$CI0.975xleft<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_xleft_d0)/numsims

hassell_extrisk_d0$CI0.025xright<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_xright_d0)/numsims
hassell_extrisk_d0$CI0.975xright<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_xright_d0)/numsims

hassell_extrisk_d0$CI0.025mleft<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_mleft_d0)/numsims
hassell_extrisk_d0$CI0.975mleft<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_mleft_d0)/numsims

hassell_extrisk_d0$CI0.025mright<-qbinom(p=0.025,size=numsims,prob=hassell_extrisk_d0$risk_mright_d0)/numsims
hassell_extrisk_d0$CI0.975mright<-qbinom(p=0.975,size=numsims,prob=hassell_extrisk_d0$risk_mright_d0)/numsims

pdf(paste(resloc,"hassell_extrisk_d0_extremenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_xright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025xright,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975xright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()

pdf(paste(resloc,"hassell_extrisk_d0_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mleft_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mleft,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mleft,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted",col="darkgrey")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_mright_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025mright,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975mright,angle=90,length=0.1,col="blue",code=3)
legend("topleft", legend=c("Hassell"), horiz=F, bty='n',cex=1.8)  
mtext(paste0("a = ",a,", b = ",b),side = 3, line=-16, adj=0.9, cex=1.8, col="black")
legend("bottomright",legend=bquote(sigma==.(scl)), horiz=F,bty='n',cex=1.8)
#legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

msmith_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist)),
                              NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store 
                                                                                     # ext risk at dispersal d=0 for all r
colnames(msmith_extrisk_d0)<-c("r","risk_xleft_d0","risk_xright_d0","risk_mleft_d0","risk_mright_d0")

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_msmith_local<-abind(res_msmith_local,temp_mat,along = 3)

    msmith_extrisk_d0$risk_xleft_d0[i]<-ss$risk_xleft[1]
    msmith_extrisk_d0$risk_xright_d0[i]<-ss$risk_xright[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_msmith_local)<-list(NULL,cnm,anm)

@@

    temp_mat<-cbind(ss$d_seq,ss$risk_xleft,ss$risk_xright,ss$risk_mleft,ss$risk_mright)
    res_msmith_global<-abind(res_msmith_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_xleft","risk_xright","risk_mleft","risk_mright")
dimnames(res_msmith_global)<-list(NULL,cnm,anm)
saveRDS(res_msmith_global,paste(resloc,"res_msmith_global.RDS",sep=""))
```

```{r fig_msmith_scl_0.8, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}

#-------------------------------------- plot for extreme tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_ext_risk_local_disp_extremenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))
